Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
Removed departure from nucleate boiling example from slides
removing sequential monte carlo slide

%%---------------------------------------------------------------------------%%
\begin{frame}{Physics-Based Motivation: DNB}

    \begin{column}{0.35\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{1}{ \input{dnb_schematic.pdftex_t} }
        \end{center}
        \caption{\textbf{Departure from nucleate boiling scenario.} }
      \end{figure}
    \end{column}

    \begin{column}{0.65\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.8}{ \input{dnb_example.pdftex_t} }
        \end{center}
        \caption{\textbf{Multiphysics dependency analysis of departure
            from nucleate boiling.} }
      \end{figure}
    \end{column}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Sequential Monte Carlo}

  \begin{itemize}
  \item Neumann-Ulam methods bound by the Central Limit Theorem
  \item Halton proposed an iterative residual method in 1962
  \item Iteration error decoupled from Monte Carlo error
  \item Exponential convergence (Evans,2003)
  \end{itemize}

  \[
  \ve{r}^k = \ve{b} - \ve{A}\ve{x}^k
  \]
  \[
  \ve{A}\boldsymbol{\delta}^{k} = \ve{r}^{k}
  \]
  \[
  \ve{x}^{k+1} = \ve{x}^k + \boldsymbol{\delta}^{k}
  \]

@@

  \begin{itemize}
  \item Adjoint Neumann-Ulam solver computes the correction
  \item Decouples Monte Carlo error from solution error
  \item Exponential convergence
  \item Demonstrated by Evans and colleagues to be competitive with
    Krylov methods
  \end{itemize}

>>>>

@@

@@

  \begin{itemize}
  \item Neumann-Ulam methods bound by the Central Limit Theorem
  \item Build on Halton's 1962 iterative residual method
  \item Adjoint Neumann-Ulam solver computes the correction
  \item Decouples MC error from solution error, exponential convergence
  \item Demonstrated by Evans to be competitive with Krylov methods
  \end{itemize}
